Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-08-16 doc/report/msc-report.tex
cleaned TODO's and bla's
tagged as RC1
report: expanded OLAP explanation and moved to OLAP section.

@@

Classic data warehouses use relational databases as storage. A star or snowflake
schema would be used to model the dimensions.

New techniques that have appeared include column-oriented, schema free
databases. Google's BigTable is such a database. Another new technique for
distributed processing is Google's MapReduce.

TODO:
Other techniques that have been frequently used to build data warehouses
include: A, B, and C, amongst others.

A solves distributed computing by ...
B is blablabla ...
The framework C was ...

@@

TODO: HBase was benchmarked (the benchmarks was similar to the ones found in the
BigTable paper?). NEEDS DATA!!

>>>>

Modelling OLAP cubes can be done in different ways, using different techniques.
The two main techniques are: MOLAP\footnote{Multidimensional On-Line Analytical
Processing} (or just OLAP), and ROLAP\footnote{Relational On-Line Analytical
Processing}. Data warehouses designed after the MOLAP principle use optimized
multi-dimensional array storage whereas ROLAP data warehouses use relational
databases as storage. When designing a ROLAP data warehouse a star or snowflake
schema would be used to model the dimensions.

@@

One new techniques which can be used for OLAP data warehouses include Google's
BigTable, which is a distributed column-oriented schema-less database.

Google's MapReduce is a new technique for distributed parallel computations.

@@
